### 2024-11-19 README.Rmd
update README
update READEME

# hatchR

<!-- badges: start -->

<!-- badges: end -->

## Overview

@@

## Installation

You can install the development version of hatchR from [GitHub](https://github.com/) with:

@@

## Usage

@@

`hatchR` suggests the following **R** Packages:

* `ggplot2` - for vignette vizualizations.
* `lubridate` - for date-time manipulation.
* `knitr`: For vignette building.
* `rmarkdown`: For vignette building.
* `testthat`: For unit testing.

## Getting help

If you encounter a clear bug, please file an issue with a minimal reproducible example on [GitHub](https://github.com/bmait101/hatchR/issues). For questions and other discussion, please reach out to the package authors: [Morgan Sparks](morgan.sparks@usda.gov), [Bryan Maitland](bryan.maitland@usda.gov).

@@

## Disclaimer

>>>>

<!-- badges: start -->
<!-- badges: end -->

# hatchR: Predicting Fish Developmental Phenology

@@

## Citation

If you use `hatchR` in a formal publication or report, please cite it. Citing `hatchR` lets us devote more resources to it in the future. View the `hatchR` citation by running
```r
citation(package = "hatchR")
```

## Installation Instructions

You can install the development version of `hatchR` from [GitHub](https://github.com/) with:

@@

## Contributing to `hatchR`

We encourage users to report bugs and/or contribute to `hatchR`. For more detail on how to do this, please see our contributing guide (`CONTRIBUTING.md`).

## Getting Help

There are several ways to get help with `hatchR`:

1. Open a GitHub issue [link here](https://github.com/bmait101/hatchR/issues).
2. Email the hatchR support team ([Morgan Sparks](morgan.sparks@usda.gov), [Bryan Maitland](bryan.maitland@usda.gov))
3. Post on a support website like Stack Overflow or Cross Validated.

## Example Usage

To come...

## Imported Packages

`hacthR` imports the following **R** packages:

* dplyr: For data manipulation.
* ggplot2: For vignette visualizations.
* lubridate: For working with dates.
* tibble: For creating tibbles as output for various functions.
* modelr: For modeling functions.
* rlang: For `.data` usage.
* stats: For various modeling functions (e.g., `confint()`).
* utils: For various utility functions.

@@

`hatchR` suggests the following **R** packages:

* knitr: For vignette building.
* readr: For reading in data.
* rmarkdown: For vignette building.
* testthat: For unit testing.

@@

## USDA Disclaimer
